### 2017-07-14 architecture.tex
Arch edits

To address the concerns outlined in the previous section we introduce two
new abstractions: safe collections, an abstraction that encapsulates
a dataset and the set of policies that govern its use; and stewards, privileged users
to manage safe collections while separating administrative from infrastructure
administrators.  
In this model, administrators first define a safe collection and declare one 
or more stewards to manage that collection. This process transfers
all administrative responsibilities regarding access and export of data to the stewards.
%who now take ownership and responsibility for the safe collection.

@@

Datasets come with various levels of sensitivity. Selecting the policies, protocols, infrastructure, and 
software settings to ensure to ensure that individual datasets are adequately secured requires consideration
on a case-by-case basis. 
%To represent these policies, such that dataset owners can manage these considerations,
%we define safe-collections. 
Safe-collections enable system administrators to partition the key administration
aspects of managing the relationship between users (e.g., analysts) and data. 
Safe-collections encapsulate the data-store in which a dataset will reside, and a consistent set of policies
that controls access to the data-store.

Safe-collections are defined with policies that govern limits as well as access to, and use of, 
data in that collection. They specifically regulate access, usage, and data export.
The policies supported by safe-collections are as follows:

\textbf{SecurityClass:} A binary classification that enables or disables
the safe collection. Setting to \texttt{Public} means that the data is freely
accessible and no other policies can be set.  Setting to \texttt{Private}
requires that the subsequent policies are set.

\textbf{Classification:} Categorizes the type of data stored in the 
safe collection including specifying that the data is controlled by
a license or that the data is subject to regulations (e.g., HIPAA or FEDRAMP).

@@

% Why do we have them / inital role
As that number of datasets managed by \NAME increase it is crucial that administrative
tasks are distributed to individual collection administrators. This separates
concerns from those that operate \NAME and those that manage the data stored in \NAMENS.
Stewards play a leadership role in evaluating the disclosure risks associated with a
dataset and codifying the security protocols protecting the safe-collection.

Stewards are responsible for activities such as approving access to a collection, reviewing
export requests, and managing policies on the collection. Users (e.g., analysts) can discover
and then obtain access to safe collections by listing available safe collections and requesting
access to individual collections. 
Stewards are presented with a list of user requests and must explicitly approve access
for a specific duration. Throughout the duration of a user's access to a collection
stewards may review their actions and revoke access at any time. When users attempt
to export data from an export controlled safe-collection, the data is not immediately
accessible to the user. Rather, the exported data is collected and stored privately
such that a steward can approve the export request. Finally, approved data exports
are turned over to the user.

@@

Here we describe the two most common flows introduced by this model:

@@

Bob an analyst authenticates on the system and requests access to a private safe-collection.
The request is now visible on the stewarship dashboard of all stewards. Alice, a steward for the requested
safe-collection approves the request for n days. The approval process adds the appropriate policies to the
safe-collection granting access to Bob. Bob now can submit tasks via the  REST api, that specify data-items
from the safe-collection as inputs. The REST api marks the task as export controlled since it draws results
from an export controlled safe-collection. The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
his credentials requests data from the safe-collection. Since Bob now has read privileges for the
safe-collection, the data is fetched to the worker node, on which the analysis task is executed.
Upon completion, the worker node puts the generated results under the outputs directory of the safe-collection
since the task used export controlled data. Bob's analysis is now complete, but he is unable to view the
results. This flow is show in \figurename~\ref{fig:flow1}

@@

Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
results, so he issues a request for export. Alice, sees a new export request on her dashboard. Alice assumes
the steward role with a fresh authenticated token, and accesses the results and the complete description
of Bob's analysis task. Once Alice deems the results safe for export, she initiates data export. \NAME
services use Alice's temporary credentials to transfer the results from the safe-collection to a public
safe-collection and updates the task information with new location of the results. Bob can now log on
and view or download the results. This flow is show in \figurename~\ref{fig:flow2}

>>>>

To address the concerns outlined in the previous section we introduce two
new abstractions: safe collections, an abstraction that encapsulates
a dataset and the set of policies that govern its use; and stewards, privileged users
to manage safe collections while separating management of data from infrastructure.  
In this model, administrators first define a safe collection and declare one 
or more stewards to manage that collection. This process transfers
all administrative responsibilities regarding access to, and export of, data to the stewards.
%who now take ownership and responsibility for the safe collection.

@@

Selecting the policies, protocols, infrastructure, and 
software settings to ensure that individual datasets are adequately secured requires consideration
on a case-by-case basis. 
%To represent these policies, such that dataset owners can manage these considerations,
%we define safe-collections. 
Safe collections enable system administrators to partition the key administration
aspects of managing the relationship between data and users (e.g., analysts who use that data). 
Safe collections encapsulate the data-store in which a dataset resides, and a consistent set of policies
that controls access to that dataset.

Safe collections are defined with policies that govern limits as well as access to, and use of, 
data in that collection. They specifically regulate access, usage, and data export.
The policies supported by safe-collections are as follows:

\textbf{SecurityClass:} A binary classification that specifies the constraints
on accessing data in that collection. Setting to \texttt{Public} means that the data is freely
(but securely) accessible to a set of permitted users and no other 
data administration policies can be set.  Setting to \texttt{Private}
requires that safe collection policies are set.

\textbf{Classification:} Categorizes the type of data stored in the 
safe collection including specifying that the data is controlled by
a license or that the data is subject to regulations (e.g., HIPAA or FEDRAMP).
This information is used by stewards and administrators when 
managing a safe collection.

@@

% Why do we have them / inital role
%As that number of datasets managed by \NAME increase it is crucial that administrative
%tasks are distributed to individual collection administrators.

Safe collection stewards are a specialized role that aims to separate
concerns from those that operate \NAME and those that manage the data stored in \NAMENS.
Stewards play a management role in evaluating the disclosure risks associated with a
dataset and codifying the security protocols protecting the safe collection.
Thus, for datasets with particular data use agreements or restrictions, they 
are responsible for ensuring all requirements are met. In the event of a
data breach or data loss, they are responsible for following appropriate
mitigation plans.

Stewards are responsible for activities such as approving access to a collection, reviewing
export requests, and managing policies on the collection. 
As described above, stewards are pre-associated with a particular safe collection by
way of a specialized role and mapping to a collection's storage layer. 
External users (e.g., analysts) can discover
and then obtain access to safe collections by listing available safe collections and requesting
access to individual collections.
Stewards for a safe collection are presented with a list of user requests and must explicitly approve access
for a specific duration. Throughout the duration of a user's access to a collection
stewards may review their actions and revoke access at any time. When users attempt
to export data from an export controlled safe-collection, the data is not immediately
accessible to the user. Rather, the exported data is collected and stored privately
such that a steward can approve the export request.

@@

Here we describe the two most common flows introduced by the safe collection model:

@@

Bob, an analyst, authenticates to \NAME and requests access to a private safe collection.
The request is added to the stewarship dashboard and is visiable to all stewards
of that collection. Alice, a steward for the requested
safe collection views and then approves Bob's request for a period of $n$ days. 
The approval process adds the appropriate policies to the
safe collection granting access to Bob. Bob now can submit analysis tasks, via 
\NAMENS's REST API, that specify data items from the safe collection as inputs. 
The REST API marks the analysis task as export controlled since it draws results
from an export controlled safe collection. 
The submitted task is posted to an internal queue from which a
worker node in the \NAME private subnet picks up Bob's task. The worker node assumes Bob's identity and with
his credentials requests data from the safe collection. Since Bob now has read privileges for the
safe collection, the data is fetched to the worker node, on which the analysis task is executed.
Upon completion, the worker node puts the generated results in the export-controlled 
output directory of the safe collection as the task used export controlled data. 
Bob's analysis is now complete, but he is unable to view the
results as they require steward approval. This flow is show in \figurename~\ref{fig:flow1}

@@

Once Bob's analysis task is complete Bob realizes that he requires export approval before he may view the
results, so he issues a request to export his results. Alice, one of the collection's stewards, recieves
the export request on her dashboard. Alice assumes
the steward role with a fresh authenticated token, and accesses the results and the complete description
of Bob's analysis task. Alice reviews the data and the analysis to determine if the results are
safe for export. When she is satisfied with Bob's process, she initiates data export. \NAME
uses Alice's temporary credentials to transfer the results from the safe collection to a public
safe collection, accessible only to Bob, and updates the task information with new location of the results. Bob can now log on
and view or download the results. This flow is show in \figurename~\ref{fig:flow2}
